### 2017-05-11 paper/paper.tex
Wrote basic theory

\section{Introduction}
\subsection{Background}
Taking a collective decision as a population is difficult. To solve this issue, voting systems with defined rules are used. They are used to show common preferences within a population, for example what politician a population wants to see elected. Several types of systems have been designed and there are a myriad of variations of those systems. They range from simple methods such as “most votes win” to complex processes that can only be practically carried out by a computer. However, practically all voting systems are algorithmic in nature, which makes them interesting to study for both Computer Scientists and Mathematicians. When deciding on what systems that shall be used, it is useful to know what differences and similarities they have.
\subsection{Purpose}
The purpose of this essay is to evaluate differences and similarities in terms of election results in three different voting systems: Single Transferable Vote (STV), First-Past-The-Post (FPTP) and the Schulze Method. This paper will only be examining and discussing differences and similarities in the results of the methods, not touching on how practically feasible the methods might be in actual election.
\section{Theory}
Theory will be here some day

@@

\section{Metrics for evaluating results}

@@

\subsection{Standard deviation}

@@

\subsection{Misrepresentation}

@@

\subsection{Most likely winners}

>>>>

\section{Introduction}
\subsection{Background}
Taking a collective decision as a population is difficult. To solve this issue, voting systems with defined rules are used. They are used to show common preferences within a population, for example what politician a population wants to see elected. Several types of systems have been designed and there are a myriad of variations of those systems. They range from simple methods such as “most votes win” to complex processes that can only be practically carried out by a computer. However, practically all voting systems are algorithmic in nature, which makes them interesting to study for both Computer Scientists and Mathematicians. When deciding on what systems that shall be used, it is useful to know what differences and similarities they have.
\subsection{Purpose}
The purpose of this essay is to evaluate differences and similarities in terms of election results in three different voting systems: Single Transferable Vote (STV), First-Past-The-Post (FPTP) and the Schulze Method. This paper will only be examining and discussing differences and similarities in the results of the methods, not touching on how practically feasible the methods might be in actual election.
\pagebreak
\section{Theory}
One would think that by testing all different voting systems and by setting up good criteria for how to evaluate them, it would be possible to come to a definitive conclusion of what system should be used. However, this is not the case. By setting up different mathematical criteria for how a voting system shall behave, it is impossible to satisfy all criteria simultaneously. This is what several theorems, most notably Arrow's Impossibility theorem outlined in 1950, show \autocite{arrow1950difficulty}. This means that any decision regarding choice of electoral system is a balance of their strengths and weaknesses. Simply put: there is no perfect voting system and never will be. This does however not mean that all voting systems are equally efficient, elegant or accurate.

There are several ways of evaluating voting methods that are used. One is the mathematical approach of evaluating what criteria are important to meet and finding elegant methods that satisfy them. Another is by testing and finding probabilities that some criteria are broken — A method that fails to meet a certain criteria only in very few cases is perhaps not that big of a problem. A third way of evaluating methods is not by mathematical criteria, but other metrics such as voter satisfaction or how likely someone is to vote tactically.
\subsection{Definitions}
\begin{itemize}
	\item A \textit{candidate} is someone a voter can vote to elect. Can also be considered as being parties that a voter can vote for.
	\item An \textit{election} is an event in which voters cast ballots to vote on candidates
	\item A \textit{seat} is something a candidate can be elected to. A candidate may for example be elected to hold a seat of parliament.
	\item An \textit{ideology} is a group that both candidates and voters can identify with. They split the whole voting population into several blocks.
\end{itemize}  

@@

\subsection{Metrics for evaluating results}

@@

\subsubsection{Standard deviation}

@@

\subsubsection{Misrepresentation}

@@

\subsubsection{Most likely winners}
